PANCHANGE_descriptives

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Fixed plotting error in the whole sample prepan retro scatterplot and changed aesthetics

whole_retro_prepan_phq_scatter <- whole_retro_prepan_scatter %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" |
           gad.pandemic_felt_feelings == "A little worse" |
           gad.pandemic_felt_feelings == "A little better" |
           gad.pandemic_felt_feelings == "Much better")

@@

whole_retro_prepan_gad_scatter %>% ggplot(aes(x = gad.sum_score_retro, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor whole sample",
                      sep=" "),
        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))

whole_retro_prepan_gad_scatter %>% ggplot(aes(x = phq.sum_score_retro, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor whole sample",
                      sep=" "),
        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))

>>>>

whole_retro_prepan_phq_scatter <- whole_retro_prepan_scatter %>% 
  filter(phq.pandemic_felt_feelings == "Much worse" |
           phq.pandemic_felt_feelings == "A little worse" |
           phq.pandemic_felt_feelings == "A little better" |
           phq.pandemic_felt_feelings == "Much better")

@@

whole_retro_prepan_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor whole sample",
                      sep=" "),
        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))

whole_retro_prepan_phq_scatter %>% ggplot(aes(x = phq.sum_score_retro, y = phq.sum_score_prepan)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor whole sample",
                      sep=" "),
        subtitle = paste("n", dim(whole_retro_prepan_phq_scatter)[1]))
